Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
spacing
rage

We consider models of physical plants expressed as ordinary differential
equations (ODEs), which we assume to be controllable~\cite{Astrom08,
astrom1997computer}:
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,
\mat{A} \in \mathbb{R}^{p \times p},
\mat{B} \in \mathbb{R}^{p \times q},
\end{align}
%
where $t \in \mathbb R_0^+$ denotes continuous time, $\mat{A}$ and $\mat{B}$
are matrices that fully characterize the dynamics of the continuous plant,
and $x(0)$ is the initial state.

We are interested in control systems with an output $\vec{y}$ that is a
linear combination of its states and inputs\footnote{Notice that since we
can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
observable.}.
%
%, which may restrict the observability of the state-space from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t),
\vec{y} \in \mathbb{R}^o,
\mat{C} \in \mathbb{R}^{o \times p},
\mat{D} \in \mathbb{R}^{o \times q}. 
\end{equation}
%
Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
time~\cite{middleton1990digital,van1978computing} at constant intervals,
whose duration we refer to as the sample time $T_s$, into the difference
equation
%
\begin{align}
\label{eq:plant}
\left\{
\begin{array}{rl}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
\end{array}
\right.
\text{ where }
\left\{
\begin{array}{l}
\mat{A}_d=e^{\mat{A}T_s}\\
\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
\end{array}
\right.,
\end{align} 
%
%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
%
$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the
initial state.  In this work we raise the standard assumption that
$\mat{D}=\mat{0}$~\cite{Astrom08}.
%
%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.

>>>>

We consider models of physical plants expressed as ordinary differential
equations (ODEs), which we assume to be controllable~\cite{Astrom08,
astrom1997computer}:
%
\begin{align}
\label{eq:ode1}
\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,\,
\mat{A} \in \mathbb{R}^{p \times p},\,
\mat{B} \in \mathbb{R}^{p \times q},
\end{align}
%
where $t \in \mathbb R_0^+$ denotes continuous time, $\mat{A}$ and $\mat{B}$
are matrices that fully characterize the dynamics of the continuous plant,
and $x(0)$ is the initial state.

We are interested in control systems with an output $\vec{y}$ that is a
linear combination of its states and inputs\footnote{Notice that since we
can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
observable.}.
%
%, which may restrict the observability of the state-space from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t),
\vec{y} \in \mathbb{R}^o,
\mat{C} \in \mathbb{R}^{o \times p},
\mat{D} \in \mathbb{R}^{o \times q}. 
\end{equation}
%
Equations~\eqref{eq:ode1}--\eqref{eq:ode2} are soundly discretized in
time~\cite{middleton1990digital,van1978computing} at constant intervals,
whose duration we refer to as the sample time $T_s$, into the difference
equation
%
\begin{align}
\label{eq:plant}
\left\{
\begin{array}{rl}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
\end{array}
\right.
\text{ where }
\left\{
\begin{array}{l}
\mat{A}_d=e^{\mat{A}T_s}\\
\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
\end{array}
\right.,
\end{align} 
%
%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
%
$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the
initial state.  In this work we raise the standard assumption that
$\mat{D}=\mat{0}$~\cite{Astrom08}.
%
%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
